---
title: "Heaviness of `shortRNA`"
format: html
editor_options: 
  chunk_output_type: console
---


# Packages
<details>
```{r}
library(pkgndep)
library(ggplot2)
library(ComplexHeatmap)
```
</details>

# Description


## Heaviness of `shortRNA`

1. **Moving `ggplot2` from Depends/Imports/LinkingTo to Suggests of `shortRNA`:**
    - Absolute measure: $v1 - v2$ where $v1$ is the total number of packages required for `shortRNA` with `ggplot2` as a necessary dependency and $v2$ is the total number of required packages if `ggplot2` is suggested.
    - Relative measure: $\frac{{v1 + a}}{{v2 + a}}$ where $a$ is a factor determining relative change in dependency counts.

2. **Moving `Biostrings` from Depends/Imports/LinkingTo to Suggests of `shortRNA`:**
    - Similar process as above but for `Biostrings` instead of `ggplot2`.


## Co-heaviness of `shortRNA`

1. **Co-action of `ggplot2` and `Biostrings` moving from Depends/Imports/LinkingTo to Suggests of `shortRNA`:**
    - $S_A$: Set of reduced dependency packages when only `ggplot2` is moved to Suggests.
    - $S_B$: Set of reduced dependency packages when only `Biostrings` is moved to Suggests.
    - $S_{{AB}}$: Set of reduced dependency packages when both `ggplot2` and `Biostrings` are moved together to Suggests.
    - Co-heaviness: $length(setdiff(S_{{AB}}, union(S_A, S_B)))$ measures the unique reduction in dependencies caused by the joint action of `ggplot2` and `Biostrings` moving together to suggested status in `shortRNA`.


## Calculation
```{r}
x <- pkgndep("shortRNA")
m <- co_heaviness(x)
h <- heaviness(x)
h <- data.frame(Package = names(h), Heaviness = h)
```

## Barplot of heaviness
```{r}
ggplot(data = h, aes(x = reorder(Package, Heaviness), y = Heaviness)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_bw() +
  xlab("Packages")
```


## Heatmap of co-heaviness
```{r, fig.height=8, fig.width=10}
Heatmap(m,
  name = "co-heaviness", col = viridis::cividis(n = 100),
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 10)
)
```


# Package optimization suggestions
[From `pkgndep`](https://cran.r-project.org/web/packages/pkgndep/vignettes/suggestions.html)

# References
```{r}
`%>%` <- magrittr::`%>%`
report::cite_packages(sessionInfo()) %>%
  details::details()
```

# Session info
```{r}
devtools::session_info() %>%
  details::details()
```
